Members

### 2025-09-24 members.qmd
add FK, TP, talk of Gregor (GH 250924)
Tu moved to members (GH 250924)

@@

>>>>

**[Franziska Kappenberg](https://www.imbie.uni-bonn.de/people/dr-franziska-kappenberg/)**: Institute for Medicine Biometry, Informatics and Epidemiology, University of Bonn, Bonn, Germany

@@

**Thomas Prince**: Institute for Medicine Biometry, Informatics and Epidemiology, University of Bonn, Bonn, Germany
